---
title: "optiTHERMM results"
author: "Glenn Boardman, Guy Stanley"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("2 missing data.R")
source("4 analysis.R")
source("3 descriptive.R")
library(ggplot2)
library(tidyverse)
```

# Missing data
Summary: data was recorded completely. Missing data likely has no effect on our hypotheses.

# Descriptive statistics
```{r} 

ggplot(data, aes(x = max.burn.size.treated)) + geom_bar()
```
\pagebreak

# Figures

## Figure 1 - Flow chart schematic of responses to survey by doctor role and geographical region (For manual graphic design)
\pagebreak
## Figure 2 - Graphical schematic of study design (For manual graphic design)
\pagebreak
## Figue 3 - Respondents, based on geographical location (curent examples drawn by hand but could be mapped in R as coordinates are provided for each city)
\pagebreak
# Tables

## Table 1 - Tabulation of survey participants, their characteristics and responses by geographical region

```{r}
table1
```
\pagebreak
